Adolescent well-being in the digital age

### 2022-03-17 clean.Rmd
Also transform mobile edge values

# Transform internet edge cases
itu <- itu %>%
  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
  mutate(internet = if_else(internet == 1, .9999999, internet))

>>>>

# Transform internet edge cases
itu <- itu %>%
  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
  mutate(internet = if_else(internet == 1, .9999999, internet)) %>% 
  mutate(mobile = if_else(mobile == 0, .0000001, mobile)) %>%
  mutate(mobile = if_else(mobile == 1, .9999999, mobile))
